Check Coverage

### 2020-09-02 analysis/merge_data.Rmd
Update biotime_traits for new biotime data.

check if all bird & mammal biotime data w/id's has an elton match. There are 68 species without a match (63 are birds).
```{r}
no_trait <- biotime_data %>%
  filter(taxa %in% c("Birds", "Mammals")) %>%
  select(id, sourceName, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

and 19869 species without an ID, some of which are species codes
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, sourceName, taxa) %>%
  filter(is.na(id)) %>%
  distinct() %>%
  dim()
```

>>>>

check if all bird & mammal biotime data w/id's has an elton match. There are 24 species without a match.
```{r}
no_trait <- biotime_data %>%
  filter(taxa %in% c("Birds", "Mammals")) %>%
  select(id, sourceName, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

and 25268 species without an ID, some of which are species codes
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, sourceName, taxa) %>%
  filter(is.na(id)) %>%
  distinct() %>%
  dim()
```
